Research Proposal

### 2021-10-01 Reports/JOURNAL - Confidence Regions/ResearchProposal.tex
Eu acho que é lixo, mas vou guardando...

\usepackage[binary-units]{siunitx}
\usepackage{fouriernc}
\usepackage{amsmath,amssymb}
\usepackage{natbib}
\usepackage{bm,bbm}
\usepackage{enumitem}
\usepackage{graphicx}
\graphicspath{{./Figures/}}

@@

\citet{ANewVersatileDiscreteDistribution} proposes a flexible discrete model, the ``discretised beta'' law.
The probability function of such a random variable is
\begin{align}
\Pr(X & = x \mid \alpha, \beta, n_{\text{top}}, \zeta) = h(x) \exp\big\{ \alpha T_1(x) + \beta T_2(x) - A(\alpha, \beta) \big\}, \\
\intertext{where}
x &\in \{n_{\text{bot}}, n_{\text{bot}}+1, \dots, n_{\text{top}}\},\\
h(x) & =\frac{(n_{\text{top}} - n_{\text{bot}}+2)^2}{
(x-n_{\text{bot}}+1)	(n_{\text{top}}-x+1)	},\\
T_1(x) &= \log\frac{x-n_{\text{bot}}+1}{n_{\text{top}}-n_{\text{bot}}+2}, \\
T_2(x) &= \log\frac{n_{\text{top}}-x+1}{n_{\text{top}}-n_{\text{bot}}+2}, \\
\intertext{and}
A(\alpha,\beta) &= \log \bigg(
\sum_{i=n_{\text{bot}}}^{n_{\text{top}}} h(i) \exp\big\{ \alpha T_1(i) + \beta T_2(i)\big\}
\bigg).
\end{align}
This definition yields a model that belongs to the exponential family for any $\alpha,\beta\in\mathbbm R$.
Denote this situation $X\sim\text{dbd}(\alpha,\beta)$.

This model can also be related to the Beta distribution with parameters $\alpha$ and $\beta$.
The probability function and other utilities as, for instance, the maximum likelihood estimator for $(\alpha,\beta)$ are implemented in the \texttt{dbd} package for \texttt{R}.

@@

We do not have that information, but we may approach the problem as an inferential one.
Let $S$ be any subset of the $H\times C$ plane.
We need 
\begin{equation}
\Pr\big((\mathfrak{H},\mathfrak{C})\in S\big)
\label{Eq:Problem}
\end{equation}
for all possible combinations of the sequence length $T$, embedding dimension $D$, and time delay $\tau$.
Since we do not know the distribution of $(\mathfrak{H},\mathfrak{C})$, we will estimate~\eqref{Eq:Problem}.

@@

The Bandt-Pompe symbolization transforms each sequence of values $\bm x_i$ into a sequence of symbols $\bm \pi_i$.
We build a histogram of proportions $\bm h_i$ with the sequence of symbols $\bm \pi_i$.
Now we assume that $\bm h_i$ is an outcome of size $N$ of $X\sim\text{dbd}(\alpha,\beta)$, and we compute $\widehat\alpha_i,\widehat\beta_i$.
In this way, the sequences $\bm x_1,\bm x_2, \dots, \bm x_N$ become histograms $\bm h_1, \bm h_2, \dots, \bm h_N$ and, on the one hand, they become points $(h_1,c_1), (h_2,c_2), \dots , (h_N,c_N)$ and estimates $(\widehat\alpha_1,\widehat\beta_1), (\widehat\alpha_2,\widehat\beta_2), \dots , (\widehat\alpha_N,\widehat\beta_N)$.
We may then use $\text{dbd}(\overline{\widehat{\alpha}_i},\overline{\widehat{\beta}_i})$ distribution as a model for the histograms.
From there, we may obtain an estimate of the distribution of $(\mathfrak{H},\mathfrak{C})$.

The problem was knowing $\Pr\big((\mathfrak{H},\mathfrak{C})\in S\big)$, but $\mathfrak{H}=\mathfrak{H}(X)$  and $\mathfrak{C} = \mathfrak{C}(X)$, and we may assume that $X\sim\text{dbd}(\alpha,\beta)$, and we may estimate $(\alpha,\beta)$.
The problem becomes finding the distribution of $\big(\mathfrak{H}(X),\mathfrak{C}(X)\big)$ under $X\sim\text{dbd}(\alpha,\beta)$.

>>>>

\usepackage{siunitx}
\usepackage{fouriernc}
\usepackage{amsmath,amssymb}
\usepackage{natbib}
\usepackage{bm,bbm}
\usepackage{enumitem}
\usepackage{graphicx}
\graphicspath{{./Figures/}}

@@

\citet{ANewVersatileDiscreteDistribution} proposes a flexible discrete model, the ``discretised beta'' law.
The probability function of such a random variable is
\begin{equation}
\Pr(X  = x \mid \alpha, \beta, n_{\text{top}}, \zeta) = h(x) \exp\big\{ \alpha T_1(x) + \beta T_2(x) - A(\alpha, \beta) \big\},
\label{Eq:Probdb}
\end{equation}
where $\zeta=\text{TRUE}$ denotes that the support starts in zero ($n_{\text{bot}}=0$), otherwise it starts in one ($n_{\text{bot}}=1$), and
\begin{align}
x &\in \{n_{\text{bot}}, n_{\text{bot}}+1, \dots, n_{\text{top}}\},\\
h(x) & =\frac{(n_{\text{top}} - n_{\text{bot}}+2)^2}{
(x-n_{\text{bot}}+1)	(n_{\text{top}}-x+1)	},\\
T_1(x) &= \log\frac{x-n_{\text{bot}}+1}{n_{\text{top}}-n_{\text{bot}}+2}, \\
T_2(x) &= \log\frac{n_{\text{top}}-x+1}{n_{\text{top}}-n_{\text{bot}}+2}, \\
\intertext{and}
A(\alpha,\beta) &= \log \bigg(
\sum_{i=n_{\text{bot}}}^{n_{\text{top}}} h(i) \exp\big\{ \alpha T_1(i) + \beta T_2(i)\big\}
\bigg).
\end{align}
This definition yields a model that belongs to the exponential family for any $\alpha,\beta\in\mathbbm R$.
Denote this situation $X\sim\text{db}(\alpha,\beta, n_{\text{top}},\zeta)$.

If $\alpha,\beta>0$, we can relate the $\text{db}(\alpha,\beta, n_{\text{top}},\zeta)$ model with the (continuous) Beta distribution in the following manner:
\begin{equation}
\Pr(X=x \mid \alpha, \beta, n_{\text{top}}, \zeta) = 
\frac{1}{\kappa} f\Big(
\frac{x-n_{\text{bot}}+1}{n_{\text{top}}-n_{\text{bot}}+2}
\Big),
\label{Eq:Probdb}
\end{equation}
where
$$
\kappa = \sum_{i=n_{\text{bot}}}^{n_{\text{bot}}} f\Big(
\frac{x-n_{\text{bot}}+1}{n_{\text{top}}-n_{\text{bot}}+2}
\Big),
$$
and $f$ is the density of a Beta distribution with parameters $\alpha$ and $\beta$.

The probability function and other utilities as, for instance, the maximum likelihood estimator for $(\alpha,\beta)$, are implemented in the \texttt{dbd} package for \texttt{R}.

@@

We do not have that information, but we may approach the problem as an inferential one.
Let $S$ be any subset of the $H\times C$ plane.
We need 
\begin{equation}
\Pr\big((\mathfrak{H},\mathfrak{C})\in S\big)
\label{Eq:Problem}
\end{equation}
for all possible combinations of the sequence length $T$, embedding dimension $D$, and time delay $\tau$.
Since we do not know the distribution of $(\mathfrak{H},\mathfrak{C})$, we will model it.

Denote $\mathcal H$ the operator that transforms $\mathcal X$ into its histogram $\bm h$.
We want to know the joint distribution of $(\mathfrak{H}(\mathcal H(X)),\mathfrak{C}(\mathcal H(X)))$, where $X$ models the sequence $\mathcal X$.
Unfortunately, even knowing the distribution of $X$ under the null hypothesis (a collection of iid random variables), modelling $\mathcal H(X)$ is difficult.

All the patterns $(\pi_i)_{1\leq i\leq D!}$ are equally probable in the ideal white noise sequence.
We then use the $\text{db}(\alpha,\beta)$ model, and set $\alpha=\beta=1$, $n_{\text{top}}=D!$, and $\zeta=\text{FALSE}$ to describe $\mathcal H(X)$ under white noise.
With this, \eqref{Eq:Probdb} becomes $\Pr(\mathcal H(X)=\bm h)=(1/D!)_{1\leq i\leq D!}$ and, most importantly, given a histogram of patterns $\bm h$ we can estimate the model which produced it.
Denote this situation $\mathcal H(X)\sim\text{db}_0$.

Questions: given that $\mathcal H(X)\sim\text{db}_0$, what is the joint distribution of $(\mathfrak{H}(\mathcal H(X)),\mathfrak{C}(\mathcal H(X)))$?

@@

The Bandt-Pompe symbolization transforms each sequence of values $\bm x_i$ into a sequence of symbols $\bm \pi_i$.
We build a histogram of proportions $\bm h_i$ with the sequence of symbols $\bm \pi_i$.
Now we assume that $\bm h_i$ is an outcome of size $N$ of $X\sim\text{db}(\alpha,\beta)$, and we compute $\widehat\alpha_i,\widehat\beta_i$.
In this way, the sequences $\bm x_1,\bm x_2, \dots, \bm x_N$ become histograms $\bm h_1, \bm h_2, \dots, \bm h_N$ and, on the one hand, they become points $(h_1,c_1), (h_2,c_2), \dots , (h_N,c_N)$ and estimates $(\widehat\alpha_1,\widehat\beta_1), (\widehat\alpha_2,\widehat\beta_2), \dots , (\widehat\alpha_N,\widehat\beta_N)$.
We may then use $\text{db}(\overline{\widehat{\alpha}_i},\overline{\widehat{\beta}_i})$ distribution as a model for the histograms.
From there, we may obtain an estimate of the distribution of $(\mathfrak{H},\mathfrak{C})$.

The problem was knowing $\Pr\big((\mathfrak{H},\mathfrak{C})\in S\big)$, but $\mathfrak{H}=\mathfrak{H}(X)$  and $\mathfrak{C} = \mathfrak{C}(X)$, and we may assume that $X\sim\text{db}(\alpha,\beta)$, and we may estimate $(\alpha,\beta)$.
The problem becomes finding the distribution of $\big(\mathfrak{H}(X),\mathfrak{C}(X)\big)$ under $X\sim\text{db}(\alpha,\beta)$.
